Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-30 journal/article.tex
Editing: T: Training, coaching

@@

\subsubsection{Transformation activities}

During transformation periods organizations conducted activities aimed towards
creating change. Examples on such activities are piloting new models, seminars
and workshops, training, and coaching on new models.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1, P2, P3, P6, P8, P9, P16, P18, P23, P27, P29,
                P33, P36, P39, P40, P41, P45, P46, P47, P50, P52  \\  % 21
        Pilot programs and other piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\  % 22
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_activities}
\end{table}

@@

Coaches were driving the agile push [P2].

Coaching was considered very important at project start. Otherwise there may be
severe long term consequences [P8].

Coaching was also seen as an important success factor [P29, P33].

The agile adoption required coaches [P47].

@@

@@

[P36]
* Coaches: Coaches from a subcontractor
* How: The coached drive the project
* How: Mentor in-house leads to take lead as soon as possible
* How: Retrospect and adapt
* When: The need for coaches disappeared gradually
* The coach role was apparently seen as the lead of the project

@@

>>>>

* What is coaching? Why is it done?

@@

\subsubsection{Training, coaching, and awareness}

During transformation periods organizations invested in activities aimed to
incorporate the new model into the thinking of people. People were new to agile
methods, and a common understanding needed to be created. Training, coaching,
and public events were used for communicating the new model to a significant
part of the organization. Describing the use of training and coaching was a very
prominent facet in transformation cases.
Table \ref{table:transformation_training} summarizes activities that
organizations use for deepening the understanding and awareness of the new
development process being applied.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1, P2, P3, P6, P8, P9, P16, P18, P23, P27, P29,
                P33, P36, P39, P40, P41, P45, P46, P47, P50, P52  \\  % 21
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Coaching was a typical way for steering the agile adoption.
In addition to training, a coaching approach was usually used to teach how to
work in an agile environment. As agile lacks rigorous prescriptions and builds
on human interactions, it is best learned in practice while a coach is giving
advice.

Coaches were driving the agile push [P2, P36], and advocating agile methods [P45].

Coaching was considered very important at project start [P8, P33, P46]. Otherwise
there may be severe long term consequences [P8].

Coaching was also seen as an important success factor [P29, P33].
The coach ensured that transformation would be successful [P16].

Having a impartial third party to rely on was a key success factor [P29].

Having too little coaches [23].

The agile adoption required coaches, especially at the start of agile projects
[P8, P46, P47].

@@

As the agile way of working penetrated the organization the need for coaching
was decreasing [P36].

Some cases presented building of a coach community as an integral part of the
agile adoption [P47, P23].

@@

[P36]
* Coaches: Coaches from a subcontractor
* How: The coaches drive the project
* How: Mentor in-house leads to take lead as soon as possible
* How: Retrospect and adapt
* When: The need for coaches disappeared gradually
* The coach role was apparently seen as the lead of the project

@@

\subsubsection{Piloting}

It was typical that before taking the transformation to full scale the new model
was tested in use in the organization specific environment.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Pilot programs and other piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\  % 22
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_activities}
\end{table}
